\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-27 notes/2loopNLSM.tex
Fixed typo Kezhu found

\section{Background}\label{background}
To set the stage, in this section we provide an overview of
color-kinematics duality -- both the on-shell and off-shell
constructions. We then detail a color-dual boostrap approach for
constructing integrands in theories for which the fully off-shell kinematic
algebra has not yet been identified, like Yang-Mills and NLSM.
\subsection{Color-dual Amplitudes}\label{onShellCK}

>>>>

\section{Background}\label{background}
To set the stage, in this section we provide an overview of
color-kinematics duality -- both the on-shell and off-shell
constructions. We then detail a color-dual bootstrap approach for
constructing integrands in theories for which the fully off-shell kinematic
algebra has not yet been identified, like Yang-Mills and NLSM.
\subsection{Color-dual Amplitudes}\label{onShellCK}
